---
title: "DA Project, Phase 2: Collecting Data"
author: "Behnaz Hosseini - 91100232"
output: 
  html_document:
    code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(dplyr)
library(magrittr)
library(data.table)
library(RDota2)

options(scipen = 999)
```

## Collecting Data
Initially, I was going to scrape data from [DOTABUFF](https://www.dotabuff.com/), but it proved to be an arduous and buggy procedure. So with further research, I came across the official R Steam API client for Dota2, RDota2.  
After the installtion, to use the package I needed a Steam Key, which I got from [Steam Community](https://steamcommunity.com/login/home/?goto=%2Fdev%2Fapikey) using my Steam account. (As the Key is confidential data, I ommited the Key registering procedure which was done using `key_actions()`)

### Get league listing (version 6.88, 12/6/2016 - 11/12/2016)
```{r, eval = FALSE}
all_leagues = as.data.frame(get_league_listing()$content)

pro_leagues = all_leagues %>%
  filter(name %in%
           c("The Boston Major 2016",
             "Northern Arena BEAT Invitational presented by Bell",
             "MarsTV Dota 2 League 2016",
             "The International 2016",
             "The Summit 5",
             "Nanyang Championships Season 2",
             "ESL One Frankfurt 2016",
             "World Cyber Arena 2016 S1",
             "World Cyber Arena 2016 S2",
             "World Cyber Arena 2016 S3",
             "ROG MASTERS 2016",
             "Dota 2 Professional League 2016",
             "Shanghai Dota2 Open S2",
             "World Electronic Sports Games International",
             "DOTA2 ACE Provisional",
             "NEA2016")) %>%
  select(name, leagueid)

```

```{r, eval = FALSE}
matches = data.frame()
for (l in 1:nrow(pro_leagues)) {
  lid = pro_leagues[l,"leagueid"]
  league_games = get_match_history(league_id = lid)
  league_games = league_games$content
  
  tmp = data.frame()
  for (m in 1:length(league_games$matches)) {
    curr_match = league_games$matches[[m]]
    if(curr_match$series_id != 0){
      tmp = tmp %>% rbind(as.data.frame(curr_match))}
  }
  tmp = cbind(league_id = lid, tmp)
  matches = matches %>% rbind(tmp)
}

remove(lid,league_games,l,curr_match,tmp,m)
```

### Init. for getting match details
```{r, eval = FALSE}
match_ids = matches$match_id
gen_details_matches = data.frame(stringsAsFactors = F)
pick_ban_matches = data.frame(stringsAsFactors = F)
players_matches = data.frame(stringsAsFactors = F)
to_be_del_matches = list()

mis_team_id = data.frame()
mis_team_id[1,1] = 3331948
mis_team_id[1,2] = "LGD.Forever Young"
mis_team_id[2,1] = 2856589
mis_team_id[2,2] = "Valkyrie eSports"
mis_team_id[3,1] = 3318843
mis_team_id[3,2] = "LW"
mis_team_id[4,1] = 3259967
mis_team_id[4,2] = "BnB"
mis_team_id[5,1] = 3321220
mis_team_id[5,2] = "T Show"
mis_team_id[6,1] = 3326680
mis_team_id[6,2] = "Horde"
mis_team_id[7,1] = 3336725
mis_team_id[7,2] = "Rampage Gaming"
colnames(mis_team_id) = c("id","name")
```

### Backup
```{r, eval = FALSE}
p = players_matches
g = gen_details_matches
ban = pick_ban_matches
dl = to_be_del_matches

```

### Get Match Details
```{r, eval = FALSE}
nik = dim(matches)[1]
ptm <- proc.time()
for (m in 1701:nik) {
  print(m)
  
  tmp = get_match_details(match_id = match_ids[[m]])$content
  if(length(tmp) >= 30){
    players_matches = bind_rows(as.data.frame(tmp[1],stringsAsFactors = F), players_matches)
    
    if(length(tmp) == 31){ # All Pick Mode
      pb = transpose(as.data.frame(rep(NA,dim(pick_ban_matches)[2])))
      colnames(pb) = colnames(pick_ban_matches)
      pick_ban_matches = bind_rows(pb,pick_ban_matches)
      
      gen_details_matches = bind_rows(as.data.frame(tmp[2:31],stringsAsFactors = F),
                                      gen_details_matches)
      gen_details_matches[1,"radiant_captain"] = NA
      gen_details_matches[1,"dire_captain"] = NA
    } # end of All Pick Mode case
    
    else if(length(tmp) == 30 | length(tmp) == 33){ # missing radiant/dire data
      d = transpose(as.data.frame(rep(NA,dim(gen_details_matches)[2])))
      colnames(d) = colnames(gen_details_matches)
        
      if(is.null(tmp$dire_team_id)){ # missing dire data
        d[1,c(1:26)] = as.data.frame(tmp[2:27],stringsAsFactors = F)
        id = matches[m,"dire_team_id"]
        team_info = get_team_info_by_team_id(id)$content
        d[1,"dire_team_id"] = id
        
        if(length(team_info$teams) == 0){
          d[1,"dire_name"] = mis_team_id[mis_team_id$id == id, "name"]
          d[1,"dire_logo"] = NA
        }
        else{
          d[1,"dire_name"] = team_info$teams[[1]]$name
          d[1,"dire_logo"] = team_info$teams[[1]]$logo
        }
        d[1,"dire_team_complete"] = 1
        
        # d[1,c(31:32)] = as.data.frame(tmp[28:29],stringsAsFactors = F)
      }
      else if(is.null(tmp$radiant_team_id)){ # missing radiant data
        d[1,c(1:22)] = as.data.frame(tmp[2:23],stringsAsFactors = F)
        id = matches[m,"radiant_team_id"]
        team_info = get_team_info_by_team_id(id)$content
        d[1,"radiant_team_id"] = id
        
        if(length(team_info$teams) == 0){
          d[1,"radiant_name"] = mis_team_id[mis_team_id$id == id, "name"]
          d[1,"radiant_logo"] = NA
        }
        else{
          team_info = get_team_info_by_team_id(id)$content
          d[1,"radiant_name"] = team_info$teams[[1]]$name
          d[1,"radiant_logo"] = team_info$teams[[1]]$logo
        }
        d[1,"radiant_team_complete"] = 1
        
        d[1,c(27:30)] = as.data.frame(tmp[24:27],stringsAsFactors = F)
      }
      
      d[1,"radiant_captain"] = tmp$radiant_captain
      d[1,"dire_captain"] = tmp$dire_captain
      gen_details_matches = bind_rows(d,gen_details_matches)
      pick_ban_matches  = bind_rows(as.data.frame(tmp[30],stringsAsFactors = F), pick_ban_matches)
    } # end of missing data case
    else{ # all normal
    gen_details_matches = bind_rows(as.data.frame(tmp[2:33],stringsAsFactors = F),
                                    gen_details_matches)
    pick_ban_matches  = bind_rows(as.data.frame(tmp[34],stringsAsFactors = F), pick_ban_matches)
    }
  } # end of length(tmp) >= 30
  else{ # too much missing data
    to_be_del_matches = append(m,to_be_del_matches)
  }
}

proc.time() - ptm

```

### Restore
```{r, eval = FALSE}
players_matches = p
gen_details_matches = g
pick_ban_matches = ban
to_be_del_matches = dl
```

### Arrange df, remove unwanted variables, add match_id col
```{r, eval = FALSE}
matches_detail = arrange(gen_details_matches,-row_number())
picks_bans     = arrange(pick_ban_matches,-row_number())
players_detail = arrange(players_matches,-row_number())

# rm(list=setdiff(ls(), c("all_leagues","pro_leagues","matches","matches_detail",
                        # "picks_bans","players_detail","tbd")))

picks_bans = cbind(match_id = matches_detail$match_id,picks_bans)
players_detail = cbind(match_id = matches_detail$match_id,players_detail)
```

### Clean matches df up
```{r, eval = FALSE}
tbd = data.frame()
for (i in 1:length(to_be_del_matches)) {
tbd[i,1] = matches[to_be_del_matches[[i]], "match_id"]
}

matches = matches %>% filter(!(match_id %in% tbd$V1))

matches_detail[,c(33:36)] = NULL
picks_bans[,c(82,83)] = NULL
```

### Get Heroes and Items data
```{r, eval = FALSE}
items = as.data.frame(get_game_items()$content)
heroes = as.data.frame(get_heroes()$content) %>% arrange(id)
```


